Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-15 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.5.0, add fix typo.

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Read \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016learning}'s model.

@@

  Read \etal ~\cite{read2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.

@@

In summary, randomly choose 10 movies as a test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Read \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide reasonable predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Read \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the models.}
\end{table}

@@

According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Read \etal's model.

>>>>

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
  the mapping ability of the CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal ~\cite{reed2016learning}'s model.

@@

  Reed \etal ~\cite{reed2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.

@@

In summary, randomly choose 10 movies as a test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide reasonable predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Reed \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the models.}
\end{table}

@@

According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.
